(Tentative) Calculating Green Function

### 2016-09-04 Green function/green-f.tex
Updating Chapter 3 of Green function.

\begin{thebibliography}{1}
    \bibitem{dissertation} 
        \href{https://sundoc.bibliothek.uni-halle.de/diss-online/07/07H039/prom.pdf}{Electronic Transport in Mesoscopic Systems}, 
        by von Georgo Metalidis. (Link found via Google)
\end{thebibliography}
\section{Chapter 2 - 2 Landauer-Büttiker formalism}
\label{sec:Chapter_2_-_2_Landauer-Buttiker_formalism}

@@

\printnomenclature
\section{License}
The entire content of this work (including the source code
for TeX files and the generated PDF documents) by 
Hongxiang Chen (nicknamed we.taper, or just Taper) is
licensed under a 
\href{http://creativecommons.org/licenses/by-nc-sa/4.0/}{Creative 
Commons Attribution-NonCommercial-ShareAlike 4.0 International 
License}. Permissions beyond the scope of this 
license may be available at \url{mailto:we.taper[at]gmail[dot]com}.
\end{document}

>>>>

\section{Chapter 2 - 2 Landauer-Büttiker formalism}
\label{sec:Chapter_2_-_2_Landauer-Buttiker_formalism}

@@

Here in this chapter the author presents the fundamental Hamiltonian of
the system under consideration.
\marginpar{
    Given the formula mentioned in previous chapter, the Hamiltonian
    presented here seemed extraneous. Maybe the author wants to examine
    the physics in more detail.
}

The process to obtain the Hamiltonian is discretization the Hamiltonian
in continuous case, quite the reverse of the first few chapters of
A. Zee's QFT in a Nutshell. It should be noted that "a site may represent 
a region containing many atoms", although "this region should be small 
compared to physically relevant quantities such as the Fermi wavelength".

    \subsection{3.1 Spin-degenerate system}
    \label{sec:3.1_Spin-degenerate_system}
    Here the general Hamiltonian, using tight-binding model, is
    mentioned:
    \begin{align}
        H = &\sum_{n,m} 
            \left( t^x_{nm}\ket{n+1,m}\bra{n,m}
                +t^y_{nm}\ket{n,m+1}\bra{n,m}+h.c.\right)\nonumber\\
            &+\sum_{n,m} \epsilon_{nm}\ket{n,m}\bra{n,m}
    \end{align}

    The important thing is to determine the coefficient $t$.
    In the absence of magnetic field, $t$ is give by:
    \begin{align}
        t^x_{nm}=t^y_{nm}=-t=-\frac{\hbar^2}{2m^* a^2}
    \end{align}
    When magnetic field is present, we effect a so called Peierls
    substitution to get $t$.
    \marginpar{
        The author points to a paper, saying that it contains a
        "lucid discussion on the physics" of Peierls substitution.
        This might be something worth reading.
    }
    The result is, using Landau gauge in one dimensional under a
    homogeneous magnetic field.
    \begin{align}
        t^x_{nm} =& -t e^{i2\pi (m-1) \Phi/\Phi_0} \\
        t^y_{nm} =& -t
    \end{align}

    When the magnetic field is inhomogeneous, it is generally difficult
    to choose a gauge to calculate analytically. The author uses a
    very intuitive discretization process to approach this problem.
    The process is best illustrated by just the following picture:
    \begin{figure}[H]
        \centering
        \includegraphics[width=0.8\linewidth]{pics/{ch3.not-uniform_magnetic_field}.png}
        \caption{Not uniform magnetic field}
        \label{fig:ch3-uniform_magnetic_field.png}
    \end{figure}

    Therefore, the result is something like:
    \begin{align}
        t^x_{nm}=-t e^{i2\pi\sum_{m'<m}\Phi_{nm'}/\Phi_0}
    \end{align}
\printnomenclature
    \subsection{3.2 Including spin degrees of freedom}
    \label{sec:3.2_Including_spin_degrees_of_freedom}

    When the spin is taken into consideration, the formulation should
    be modified accordingly.

    If Zeeman/exchange splitting is considered, then:
    \begin{align}
        H_S = -\frac{1}{2}g^* \mu_B
            \sum_{nm}\ket{n,m}\bra{n,m}\otimes (B^{eff}_{nm}\cdot\sigma)
    \end{align}
    Not that the magnetic field strength here is only "effective".

    If Spin-orbit coupling is taken into consideration,
    \footnote{
        In my opinion, this is essentially all about Spin-Magnetic 
        field coupling, not just Spin-Orbital coupling.
    }
    the following Hamiltonian should be considered:
    \begin{align}
        H_{SO}= \lambda P\cdot (\bigtriangledown V \times \sigma)
        \label{eq:ch3.SO_coupling}
    \end{align}
    Here $P$ is the mechanical momentum operator, $\sigma$ is the
    three pauli spin matrix $(\sigma_x, \sigma_y, \sigma_z)$.

    The tight-binding version of this is too complicated to be presented
    here, it is on page 16, equation (3.20).

    One additional consideration is the Rashba spin-orbit coupling.
    This is the peculiar result of electrons trapped in a two
    dimensional surface. In the $Z$ direction, with $Z$ perpendicular
    to the 2 dimensional plane, the potential looks like something
    below, called a triangular potential:
    \begin{figure}[H]
        \centering
        \includegraphics[width=0.6\linewidth]{pics/{ch3.rashba_spin-orbit_effect}.png}
        \caption{Conduction band at the interface of a semiconductor 
            heterostructure. Band bending creates a potential well 
            $V(z)$ confining the electrons to the XY plane. The asymmetry 
            of this well leads to Rashba spin-orbit coupling.}
        \label{fig:ch3-orbit_effect.png}
    \end{figure}
    It is pretty obvious, by equation \ref{eq:ch3.SO_coupling}, that
    this potential is going into our Hamiltonian.
    The result in tight-binding model is yet another complicated
    Hamiltonian, not to be presented here, numbered equation (3.23)
    on page 18.

\section{Anchor}

\begin{thebibliography}{1}
    \bibitem{dissertation} 
        \href{https://sundoc.bibliothek.uni-halle.de/diss-online/07/07H039/prom.pdf}{Electronic Transport in Mesoscopic Systems}, 
        by von Georgo Metalidis. (Link found via Google)
\end{thebibliography}
\section{License}
The entire content of this work (including the source code
for TeX files and the generated PDF documents) by 
Hongxiang Chen (nicknamed we.taper, or just Taper) is
licensed under a 
\href{http://creativecommons.org/licenses/by-nc-sa/4.0/}{Creative 
Commons Attribution-NonCommercial-ShareAlike 4.0 International 
License}. Permissions beyond the scope of this 
license may be available at \url{mailto:we.taper[at]gmail[dot]com}.
\end{document}
